---
title: "Exploring Patterns in Time Series Data with the SPATFunctions Package"
author: "Gottfried Pestal, Michael Barrus"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring Patterns in Time Series Data with the SPATFunctions Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---





# Introduction



## General Purpose

Patterns between time series


## Specific topic area


Built for and tested with salmon population time series, which have the following
typical characteristics:

* usually short and gappy 
* b
* c 

## Previous Work 
   
* Peterman and Dorner (2012): 64 sockeye stocks, correlation in spawner-recruit residuals
* Dorner, Catalano and Peterman (2018):  24(?) Chinook stocks, DFA to find clusters in R/S data
   
   
   
## Package Design 


Focus of the package function


guiding principles for the  design  of *{SPATFunctions}*

* exploratory and versatile
* fast
* easy integration into shiny apps



#  Example 1:  Spawner-Recruit Data for 19 Stocks


```{r}
# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
```


```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```
    
   
   
   
   
   
   
